Modeling ice-shelf cavities and tabular icebergs using Lagrangian elements

### 2018-09-09 Lagrangian_MISOMIP.tex
Upadate

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
\caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.  The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz} and \ref{fig:meridional_velocity_snapshots}, respectively.}}
\end{center}
%FIgure created by \end{center}
\label{fig:SST_snapshots}
\end{figure}
 \clearpage

@@

\begin{figure}
\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t1_t15_t50.png}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x153.png}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment. Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. \textcolor{red}{Could show 1,14 and 50 days after calving to be consistent with the other Figures. But this figure is more interesting}}}
\end{center}
\label{fig:meridional_velocity_snapshots}
\end{figure}
 \clearpage

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
\caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation. The anomalies are relative to pre-calving temperatures. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving. Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.  The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz}, respectively.}}
\end{center}
%FIgure created by \end{center}
\label{fig:SST_snapshots}
\end{figure}
 \clearpage

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
%\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment. Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving. The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a. \textcolor{red}{Could show 1,14 and 50 days after calving to be consistent with the other Figures. But this figure is more interesting}}}
%\end{center}
%\label{fig:meridional_velocity_snapshots}
%\end{figure}
% \clearpage
